% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[none]{hyphenat}
\usepackage{ragged2e}
\usepackage{anysize}
\marginsize{0.5in}{1.9in}{0.5in}{0.5in}
\begin{document}

\name{Manu K. Gupta}
% \address used twice to have two lines of address
\address{Email: manu.gupta@iitb.ac.in}
\address{manu.gupta@iitb.ac.in}
\address{http://www.ieor.iitb.ac.in/users/manu}

 
\begin{resume}
 
\section{OBJECTIVE}   To develop and improvise optimal control algorithms for complex random systems

%   To improvise the machine learning algorithms for applications in areas such as pattern recognition, etc. under dynamic learning environment
 
 
\section{EDUCATION} {\sl \textbf{Bachelor of Science}}  \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
               Lucknow Christian Degree College, Lucknow \\
                Graduated July 2009 (Grade 71\%)\\
                Concentration: Statistics, Mathematics and Computer Applications (SMCA)

{\sl \textbf{Master of Science + Doctor of Philosophy Dual Degree}}  \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
               Indian Institute of Technology, Bombay \\
                Currently Pursuing (Joined July 2009) \\
                Department: Industrial Engineering and Operations Research\\
                Concentration: Optimization of stochastic systems (CGPA: 8.66/10)
          
  
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} C, ARENA, Easy-Fit, CPLEX, R, Matlab, \LaTeX, AnyLogic \\
                {\sl Operating Systems:} GNU/Linux, Windows
                
                
\section{MAJOR \\ COURSES} Optimization Techniques, Introduction to Stochastic Models, Integer Programming,
Markov Decision Process, Selected Applications of Stochastic Systems, Analysis and Control of Queues,
Discrete Event Simulation, Engineering Statistics, Computer Programming
and Algorithms, Modelling and Computational lab, IEOR lab.

\section{RESEARCH\\
PUBLICATIONS} {\footnotesize \begin{enumerate}
\item Manu K. Gupta, N. Hemachandra, and J. Venkateswaran, \textit{Optimal pricing
and pre-emptive scheduling in exponential server with two classes of
customers}, International Conference on Optimization, Computing and
Business Analytics , Kolkata, India, Allied Publishers, pp. 103-108, 12/2012.
\item Ratnaji Vanga, Manu K. Gupta, and J. Venkateswaran, \textit{Performance Evaluation of Bat Algorithm to Solve Deterministic and Stochastic Optimization Problems}, International Simulation Conference of India, IIT Madras, Chennai, 02/2013

\item Veeraruna Kavitha, Veronique Capdevielle, and Manu K. Gupta, \textit{Small Cell Networks: Speed Based Power Allocation}, 51st Annual Allerton Conference on Communication, Control, and Computing , University of Illinois at Urbana-Champaign, Allerton Retreat Center, Monticello, Illinois, 10/2013

\item A. Rawal, Veeraruna Kavitha and Manu K. Gupta, \textit{Optimal Surplus Capacity Utilization in Polling Systems via Fluid Models}, 12th International Symposium on Modeling and Optimization in Mobile, Ad Hoc, and Wireless Networks (WiOpt) , Hammamet, Tunisia, 05/2014

\item Manu K. Gupta, N. Hemachandra and J. Venkateswaran. \textit{On completeness and equivalence of EDD and HOL-PJ dynamic priority schemes in two class M/G/1 queue} Submitted in CDC-2014.

\item Manu K. Gupta, N. Hemachandra, Bharat S. Raghav and J. Venkateswaran. \textit{On a conjecture and performance of a two class delay dependent priority queue arising from pricing surplus server capacity} Submitted in EJOR.

\item Manu K. Gupta, \textit{Pricing Server's Surplus Capacity}, Presented in IEOR day, IIT Bombay


\end{enumerate}}

\section{MAJOR
PROJECTS} \begin{enumerate}
\item Karnataka Engineering Company (KEC) (Autumn 2009)
{\footnotesize\begin{itemize}
\item Modeled an integer linear program formulation to decide optimal stockyard locations.
\item Coded the model in OPL/CPLEX Suggested optimal locations for stockyards.
\end{itemize}}
\item Simulator for analysis of queue in Rawai railway station (Autumn 2010)
{\footnotesize\begin{itemize}
\item Collected data to determine Inter arrival and service time distribution for different class of
customers.
\item Used Easy-Fit 5.4 Professional to find the best fit parameter.
\item Modelled the system using ARENA Simulation Software.
\item Proposed recommendation based on optimal parameter setting.
\end{itemize}}
\item Stochastic dynamic programming approach for airline ticketing (Autumn
2011)
{\footnotesize\begin{itemize}
\item Formulated a Markov Decision Process (MDP) model and used backward induction.
\item Used MATLAB for computational purpose.
\end{itemize}}
\item Optimal routing for Mid-day meal vehicle (Autumn 2011)
{\footnotesize\begin{itemize}
\item Modelled as mixed integer program.
\item Solved using OPL/CPLEX to find optimal route.
\end{itemize}}
\end{enumerate}

                
\section{TEACHING EXPERIENCE} {\sl as a Teaching Assistant} \\
                Indian Institute of Technology Bombay, Mumbai
                 \begin{itemize}  \itemsep -1pt %reduce space between items
  {\footnotesize               \item Modelling and Computational Lab {\scriptsize(Autumn 2011)}
                 \item IEOR Lab {\scriptsize(Spring 2012)}
                 \item Selected Applications of Stochastic processes {\scriptsize(Autumn 2012)}
                 \item Analysis and Control of Queues {\scriptsize(Spring 2013)}
                 \item Introduction to Stochastic Models {\scriptsize(Autumn 2013)}
                 \item Analysis and Control of Queues {\scriptsize(Spring 2014: Current TA)}}
                 \end{itemize} 
 Organised workshop for SAS and \LaTeX. Conducted \textit{tutorials} for Introduction to Stochastic Models in Autumn 2013.
 
 \section{SCHOLASTIC
ACHIVEMENT}
\begin{itemize}
\item Silver Medal in undergrads (06-09)
\item AIR 82 in JAM exam conducted by IITs in 2009.
\end{itemize}
\section{SEMINARS}
\begin{itemize}
\item Attended International Simulation Conference of India (ISCI) in Feb 2012 at
IIT Bombay.
\item Attended winter school on Analytics \& Optimization organised by IBM Research
India, in October 2012 at Banglore.
\item Attended International Conference on Optimization, Computing and Business Analytics (ICOCBA) in Dec 2012 at Kolkata
\item Attended Operations Management Conclave at SP Jain Institute of Management Studies and Research, Mumbai in Jan 2013.
\item Attended School on Stochastic Processes in Engineering organised by IISc
Mathematics Initiative (IMI) in March 2013.
\item Attended Workshop on High Dimensional Network Analytics organised at IISc in December 2013. 
\end{itemize}
\section{POSITION OF RESPONSIBILITY}

\begin{itemize}
\item Research Scholar Companion (2011 - 2012)  
\item Library Secretary for Hostel 12 (2012 - 2013)
\item Web Secretary for Hostel 12 (2013 - 2014)
\item Election Officer for Departmental Council Election 2014 
\end{itemize}
%\section{RESEARCH EXPERIENCE} {\sl Doctoral Student} \hfill            2009 - Till date \\
%                Indian Institute of Technology Bombay, Mumbai
%                 \begin{itemize}  \itemsep -2pt %reduce space between items
%                 \item Simulation based optimization approach in (s,S) inventory system
%                 \item Optimal pricing and scheduling of customers in single node queue
%                 \item Completeness of different multi class dynamic priority  
%                 \end{itemize} 
                
 \end{resume}

\end{document}







